A Partitioning Algorithm for Maximum Common Subgraph Problems\thanks{This work was supported by a pile of money from a funding agency.}

### 2017-02-16 paper/paper.tex
We can math inside algorithm

\Lineref{StoreIncumbent} stores the current mapping $M$ if it is large enough
to unseat the incumbent.  \Linerangeref{SetBestFutureToZero}{PruneSearch} prune
the search when a calculated upper bound (best future $\AlgVar{bf}$ plus $|M|$) is not larger
than the incumbent.

>>>>

\Lineref{StoreIncumbent} stores the current mapping $M$ if it is large enough
to unseat the incumbent.  \Linerangeref{SetBestFutureToZero}{PruneSearch} prune
the search when a calculated upper bound (best future $\AlgVar{bf}$ plus $|M|$) is not larger
than the incumbent ?? rewrite this as one line using $\sum$?.
